### 2013-12-11 finalproject/paper.tex
paper structure and beginnings

\documentclass[pdftex,letterpaper,titlepage,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0}
}

\begin{document}
  \title{The Privacy of Private Browsing}
  \author{Ashley Hedberg\thanks{\emph{Mentor:} Ming Chow, Tufts University} \\
  \href{mailto:ashley.hedberg@tufts.edu}{ashley.hedberg@tufts.edu}}
  \date{}
  \maketitle

  \begin{abstract}
  Eventually the abstract will go here.
  \end{abstract}

  \section{Introduction}
  Most modern web browsers offer some sort of private browsing mode. This is
  supposed to allow users to view web content without other users of the same
  computer being able to determine what websites were visited. What is kept
  private and what is not differs from browser to browser. An overview of the
  most common browsers for Windows and Linux is provided below.

    \subsection{Mozilla Firefox}
    Mozilla Firefox runs on both Windows and Linux operating systems. Its
    private browsing mode is known as simply Private Browsing. Mozilla explains
    that it will not save information about websites and web pages accessed in
    a private browsing session, but it also clearly states that it does not
    preserve internet anonymity and does not prevent internet service
    providers, network administrators, or websites from recording such
    information. It is possible to have both private and non-private windows
    open at the same time.\cite{verdi13}

    \subsection{Google Chrome}
    Google Chrome also runs on both Windows and Linux. Its private browsing
    mode is called incognito mode. Browsing history and downloads are not
    recorded when browsing in incognito mode, and any cookies created during
    an incognito browsing session are deleted once the last incognito window is
    closed. As with Firefox, private and non-private windows can be open at the
    same time.\cite{google13}

    \subsection{Microsoft Internet Explorer}
    Microsoft Internet Explorer only runs on Windows. Its private browsing mode
    is called InPrivate Browsing. Microsoft claims that this browsing mode
    helps to ``prevent'' pages visited, cached data, cookies, and login
    information from being stored after the browsing session terminates, but it
    only guarantees that an InPrivate Browsing session won't retain information
    about websites accessed or web searches. Once again, private and non-
    private windows can be open simultaneously.\cite{ie13}

    \subsection{Tor Browser Bundle}
    The Tor Browser Bundle runs on both Windows and Linux.

  \section{To the Community}

  \section{Applications}

  \section{Conclusion}

  \begin{thebibliography}{9}
    \bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{https://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{https://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.

  \end{thebibliography}

\end{document}

### 2013-12-11 finalproject/paper.tex
added table, need to fix apostrophes

@@
 \usepackage{hyperref}
+\usepackage{array}
 
@@
   \section{Introduction}
+    \subsection{Browser Overview}
+    The following table summarizes the web browsers that will be considered in
+    this paper. The features that a particular web browser's private mode is
+    believed to have comes from the developers of the browser. Note that all
+    browsers run on both Windows and Linux, with the exception of Internet
+    Explorer, which runs only on Windows.\cite{verdi13}\cite{google13}
+    \cite{ie13}
+
+    \begin{center}
+      \begin{tabular}{|m{'5cm'}|c|c|c|}
+        \hline
+        Property & Mozilla Firefox & Google Chrome & Internet Explorer \\
+        \hline
+        Browser history & X & X & X \\
+        \hline
+        Form data & X &  & X \\
+        \hline
+        Search bar data & X &  & X \\
+        \hline
+        Passwords & X &  & X \\
+        \hline
+        Downloads & X & X &  \\
+        \hline
+        Cookies & X & X & X \\
+        \hline
+        Cached files & X &  & X \\
+        \hline
+        Simulataneous sessions with different privacy settings & X & X & X \\
+        \hline
+        Hides activity from ISP &  &  &  \\
+        \hline
+        Hides activity from websites &  &  &  \\
+        \hline
+      \end{tabular}
+    \end{center}
+
+  This paper also discusses the Tor browser. Unlike Firefox, Chrome, and
+  Internet Explorer, the Tor browser connects users to the internet using the
+  Tor network. This does much more to preserve browsing anonymity than the
+  browsers listed above. TODO finish this\ldots lazy.
+
   Most modern web browsers offer some sort of private browsing mode. This is
@@
       Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
-      $<$\url{https://support.mozilla.org/en-US/kb/private-browsing-browse-web-
+      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
       without-saving-info}$>$.
@@
       ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
-      2013. $<$\url{https://www.google.com/intl/en/chrome/browser/
+      2013. $<$\url{http://www.google.com/intl/en/chrome/browser/
       features.html#privacy}$>$.
@@
       internet-explorer/products/ie-9/features/in-private}$>$.
+    \bibitem{tor13}
+      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
+      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$.
 

### 2013-12-11 finalproject/paper.tex
removed revised sections

@@
-\documentclass[pdftex,letterpaper,titlepage,11pt]{article}
+\documentclass[pdftex,letterpaper,11pt]{article}
 \usepackage[margin=1in]{geometry}
 \usepackage{hyperref}
-\usepackage{array}
 
@@
   \begin{abstract}
-  Eventually the abstract will go here.
+  %write this
   \end{abstract}
@@
     \subsection{Browser Overview}
-    The following table summarizes the web browsers that will be considered in
-    this paper. The features that a particular web browser's private mode is
-    believed to have comes from the developers of the browser. Note that all
-    browsers run on both Windows and Linux, with the exception of Internet
-    Explorer, which runs only on Windows.\cite{verdi13}\cite{google13}
-    \cite{ie13}
+    Currently, the most popular browsers for the Windows and Linux families of
+    operating systems are Mozilla Firefox, Google Chrome, and Microsoft 
+    Internet Explorer. (Internet Explorer runs only on the Windows family of
+    operating systems, whereas Firefox and Chrome run on both Windows and 
+    Linux.) All three of these browsers have built-in private browsing modes.
+    The features and protections provided by each of these private browsing
+    modes are summarized below.\cite{verdi13}\cite{google13}\cite{ie13}
 
     \begin{center}
-      \begin{tabular}{|m{'5cm'}|c|c|c|}
+      \begin{tabular}{|p{5cm}|c|c|c|}
         \hline
-        Property & Mozilla Firefox & Google Chrome & Internet Explorer \\
+         & Firefox & Chrome & Internet Explorer \\
+         & Private Browsing & Incognito Mode & InPrivate Browsng \\
         \hline
@@
     Tor network. This does much more to preserve browsing anonymity than the
-  browsers listed above. TODO finish this\ldots lazy.
+    browsers listed above. %finish this section
 
+    \subsection{Known Issues with Private Browsing}
+    Prior research in this area indicates that web browsers, even when used in
+    their respective private browsing modes, can leave artifacts on a user's
+    machine that can reveal their internet activities. %finish
+
+  % Remove below before final submission
+  \iffalse
   Most modern web browsers offer some sort of private browsing mode. This is
@@
     The Tor Browser Bundle runs on both Windows and Linux. 
+  \fi
 

### 2013-12-11 finalproject/paper.tex
fixed spacing and rewrote beginning

@@
-\documentclass[pdftex,letterpaper,11pt]{article}
+\documentclass[pdftex,letterpaper,12pt]{article}
 \usepackage[margin=1in]{geometry}
 \usepackage{hyperref}
+\usepackage[doublespacing]{setspace}
 
@@
 }
+\setlength\parindent{0.5in}
 
 \begin{document}
+  \singlespacing
   \title{The Privacy of Private Browsing}
@@
   \begin{abstract}
-  %write this
+  Most modern web browsers have a ``private browsing'' mode that supposedly 
+  allows a user to surf the internet without leaving any traces of his or her
+  activity on his or her machine. However, the notion of ``private browsing'' 
+  offers users a false sense of security, as browsing information is often left
+  behind when a private browsing session terminates. Several researchers have 
+  already demonstrated methods of detecting this information. These include the
+  analysis of virtual and browser memory and the pagefile on Windows machines.
+  The existence of private browsing artifacts on a user’s machine raises many 
+  questions: how much privacy do web browser developers actually aim to provide
+  with ``private browsing'' modes? Are these goals accurately conveyed to the 
+  end user? And, if the user’s browsing session can be reconstructed from these
+  artifacts, how might this be exploited by digital forensics professionals? 
+  This paper seeks to answer these questions and to prove that such artifacts 
+  can be used to determine, at least in part, what a user was doing during his 
+  or her ``private browsing'' session---thereby rendering it not very private 
+  at all.
   \end{abstract}
 
+  \doublespacing
   \section{Introduction}
@@
 
+    \singlespacing
     \begin{center}
@@
         \hline
-        Hides activity from ISP &  &  &  \\
-        \hline
-        Hides activity from websites &  &  &  \\
-        \hline
       \end{tabular}
     \end{center}
+    \doublespacing
 
-    This paper also discusses the Tor browser. Unlike Firefox, Chrome, and
-    Internet Explorer, the Tor browser connects users to the internet using the
-    Tor network. This does much more to preserve browsing anonymity than the
-    browsers listed above. %finish this section
+    The private browsing modes of Firefox, Chrome, and Internet Explorer are
+    designed with the intent of preventing users of the same computer from
+    determining what someone was doing on that computer. They do not attempt
+    to keep a user's internet activities hidden from that user's internet
+    service provider (ISP), and they do not prevent websites from identifying
+    that user.\cite{verdi13}\cite{google13}\cite{ie13}
+
+    Users seeking this kind of anonymity should use the Tor browser, which
+    employs onion routing to connect a user to a destination server. In this
+    type of routing, a random path from the user to the destination is
+    constructed, and content is encrypted at each point in the path.
+    Furthermore, each point (known as a relay or node) only knows from which
+    relay any given piece of network traffic immediately came and the next
+    relay to which it is going. It does not know the original source of the
+    network traffic or its final destination. This is what allows users to keep
+    themselves and their activities anonymous using Tor in a way that the 
+    traditional web browsers cannot.\cite{tor13}
+
+    The specifics of the Tor network and how it can be used (and abused) will
+    not be considered here. It is mentioned because the Tor browser, like the
+    more common web browsers, can leave artifacts of web browsing sessions on
+    an individual's computer.
 
@@
     machine that can reveal their internet activities. %finish
-
-  % Remove below before final submission
-  \iffalse
-  Most modern web browsers offer some sort of private browsing mode. This is
-  supposed to allow users to view web content without other users of the same
-  computer being able to determine what websites were visited. What is kept
-  private and what is not differs from browser to browser. An overview of the
-  most common browsers for Windows and Linux is provided below.
-
-    \subsection{Mozilla Firefox}
-    Mozilla Firefox runs on both Windows and Linux operating systems. Its
-    private browsing mode is known as simply Private Browsing. Mozilla explains
-    that it will not save information about websites and web pages accessed in
-    a private browsing session, but it also clearly states that it does not
-    preserve internet anonymity and does not prevent internet service
-    providers, network administrators, or websites from recording such
-    information. It is possible to have both private and non-private windows
-    open at the same time.\cite{verdi13}
-
-    \subsection{Google Chrome}
-    Google Chrome also runs on both Windows and Linux. Its private browsing
-    mode is called incognito mode. Browsing history and downloads are not
-    recorded when browsing in incognito mode, and any cookies created during
-    an incognito browsing session are deleted once the last incognito window is
-    closed. As with Firefox, private and non-private windows can be open at the
-    same time.\cite{google13}
-
-    \subsection{Microsoft Internet Explorer}
-    Microsoft Internet Explorer only runs on Windows. Its private browsing mode
-    is called InPrivate Browsing. Microsoft claims that this browsing mode
-    helps to ``prevent'' pages visited, cached data, cookies, and login
-    information from being stored after the browsing session terminates, but it
-    only guarantees that an InPrivate Browsing session won't retain information
-    about websites accessed or web searches. Once again, private and non-
-    private windows can be open simultaneously.\cite{ie13}
-
-    \subsection{Tor Browser Bundle}
-    The Tor Browser Bundle runs on both Windows and Linux. 
-  \fi
 
@@
 
+  \singlespacing
   \begin{thebibliography}{9}

### 2013-12-13 finalproject/paper.tex
wrote to community and started applications

@@
-\documentclass[pdftex,letterpaper,12pt]{article}
+\documentclass[pdftex,letterpaper,titlepage,12pt]{article}
 \usepackage[margin=1in]{geometry}
@@
     \subsection{Browser Overview}
-    Currently, the most popular browsers for the Windows and Linux families of
-    operating systems are Mozilla Firefox, Google Chrome, and Microsoft 
-    Internet Explorer. (Internet Explorer runs only on the Windows family of
-    operating systems, whereas Firefox and Chrome run on both Windows and 
-    Linux.) All three of these browsers have built-in private browsing modes.
+    Currently, the most popular browsers for the Windows family of operating 
+    systems are Mozilla Firefox, Google Chrome, and Microsoft Internet 
+    Explorer. All three of these browsers have built-in private browsing modes.
     The features and protections provided by each of these private browsing
@@
 
+    \subsection{What Private Browsing Is Not}
     The private browsing modes of Firefox, Chrome, and Internet Explorer are
@@
     service provider (ISP), and they do not prevent websites from identifying
-    that user.\cite{verdi13}\cite{google13}\cite{ie13}
-
-    Users seeking this kind of anonymity should use the Tor browser, which
-    employs onion routing to connect a user to a destination server. In this
-    type of routing, a random path from the user to the destination is
-    constructed, and content is encrypted at each point in the path.
-    Furthermore, each point (known as a relay or node) only knows from which
-    relay any given piece of network traffic immediately came and the next
-    relay to which it is going. It does not know the original source of the
-    network traffic or its final destination. This is what allows users to keep
-    themselves and their activities anonymous using Tor in a way that the 
-    traditional web browsers cannot.\cite{tor13}
+    that user.\cite{verdi13}\cite{google13}\cite{ie13} Users seeking this kind 
+    of anonymity should use the Tor browser, which employs onion routing to 
+    connect a user to a destination server. In this type of routing, a random 
+    path from the user to the destination is constructed, and content is 
+    encrypted at each point in the path. Furthermore, each point (known as a 
+    relay or node) only knows from which relay any given piece of network 
+    traffic immediately came and the next relay to which it is going. It does 
+    not know the original source of the network traffic or its final 
+    destination. This is what allows users to keep themselves and their 
+    activities anonymous using Tor in a way that the traditional web browsers 
+    cannot.\cite{tor13}
 
@@
 
-    \subsection{Known Issues with Private Browsing}
-    Prior research in this area indicates that web browsers, even when used in
-    their respective private browsing modes, can leave artifacts on a user's
-    machine that can reveal their internet activities. %finish
+  \section{To the Community}
+  There are many misconceptions about private browsing. Some believe that it
+  prevents an internet service provider, network administrator, or attackers
+  engaged in packet sniffing from linking a user's internet activities to his
+  or her identity. It does not. Any and all network packets leaving the user's
+  machine contain information such as the user's IP address, which can be used
+  to determine his or her location and/or identity. Others think that private
+  browsing sessions leave absolutely no trace of their activities on their
+  local machines. As the next section of this paper will describe, this is also
+  false. Still others think that private browsing will prevent the National
+  Security Agency from tracking them on social media. It certainly does not.
+  This paper will shed some light on what private browsing sessions can and
+  cannot do, allowing internet users to think twice before exploring the web.
 
-  \section{To the Community}
+  \section{Applications: Forensics}
+  One of the biggest problems with private browsing sessions is that artifacts
+  remain on a machine after the user exits his or her internet browser. These
+  artifacts can include logon information for websites, browsing history,
+  and digital media such as images and videos---all items that you would expect
+  a private browsing session to keep private.\cite{ohana13}
 
-  \section{Applications}
+  This section will first summarize locations on a Windows machine where
+  private browsing artifacts might be found. An overview of what specific
+  artifacts were found for each browser using different forensic techniques
+  will follow. The use of SQLite to investigate specific browser artifacts will
+  then be discussed.
+
+    \subsection{Where To Look}
+
+    Focused analysis of the hard drive itself can reveal the most artifacts.
+    One private browsing experiment in which logon information, browser
+    history, and cached images were recovered obtained most of the artifacts
+    from portions of the hard disk known as \emph{free space} and \emph{slack
+    space}. Free space refers to a group of hard drive sectors (called a
+    \emph{cluster} that is not allocated to any particular file. Slack space, 
+    on the other hand, refers to the space between the end of a file and the 
+    end of the cluster in which it is stored. Hard drive clusters are of a 
+    fixed size determined by the operating system. Most of the time, when a 
+    user saves a file to his or her hard drive, the file is not exactly the
+    same size as the cluster in which the operating system puts it.
+    Furthermore, when a user ``deletes'' a file from his or her hard drive, the
+    file is not really deleted---it is simply marked as available to be
+    overwritten if necessary. If a file is eventually stored on the hard drive
+    in a cluster that used to be home to a larger (now ``deleted'') file,
+    leftover data from the old file will still exist at the end of that
+    cluster.
+
+    \subsection{Firefox}
+
+    \subsection{Google Chrome}
+
+    \subsection{Internet Explorer}
+    Internet Explorer leaves the most artifacts behind when its InPrivate
+    Browsing mode terminates.\cite{ohana13}
+
+    \subsection{Tor}
+
+    \subsection{Forensic Software}
 
@@
       2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$. 
+    \bibitem{ohana13}
+      Ohana, Donny, and Narasimha Shashidhar. ``Do Private and Portable Web 
+      Browsers Leave Incriminating Evidence? A Forensic Analysis of Residual 
+      Artifacts from Private and Portable Web Browsing Sessions.'' IEEE CS 
+      Security and Privacy Workshops (SPW), The Westin St. Francis, 
+      San Francisco, CA. 23-24 May 2013. Web. 9 Dec. 2013. $<$\url{http://www.
+      ieee-security.org/TC/SPW2013/papers/data/5017a135.pdf}$>$
 

### 2013-12-13 finalproject/paper.tex
more applications and conclusion

@@
     service provider (ISP), and they do not prevent websites from identifying
-    that user.\cite{verdi13}\cite{google13}\cite{ie13} Users seeking this kind 
-    of anonymity should use the Tor browser, which employs onion routing to 
-    connect a user to a destination server. In this type of routing, a random 
-    path from the user to the destination is constructed, and content is 
-    encrypted at each point in the path. Furthermore, each point (known as a 
-    relay or node) only knows from which relay any given piece of network 
-    traffic immediately came and the next relay to which it is going. It does 
-    not know the original source of the network traffic or its final 
-    destination. This is what allows users to keep themselves and their 
-    activities anonymous using Tor in a way that the traditional web browsers 
-    cannot.\cite{tor13}
-
-    The specifics of the Tor network and how it can be used (and abused) will
-    not be considered here. It is mentioned because the Tor browser, like the
-    more common web browsers, can leave artifacts of web browsing sessions on
-    an individual's computer.
+    that user.\cite{verdi13}\cite{google13}\cite{ie13}
 
@@
     \subsection{Where To Look}
-
     Focused analysis of the hard drive itself can reveal the most artifacts.
@@
     from portions of the hard disk known as \emph{free space} and \emph{slack
-    space}. Free space refers to a group of hard drive sectors (called a
-    \emph{cluster} that is not allocated to any particular file. Slack space, 
-    on the other hand, refers to the space between the end of a file and the 
-    end of the cluster in which it is stored. Hard drive clusters are of a 
-    fixed size determined by the operating system. Most of the time, when a 
-    user saves a file to his or her hard drive, the file is not exactly the
-    same size as the cluster in which the operating system puts it.
+    space}.\cite{ohana13} Free space refers to a group of hard drive sectors 
+    (called a \emph{cluster}) that is not allocated to any particular file.
+    Slack space,on the other hand, refers to the space between the end of a 
+    file and the end of the cluster in which it is stored. Hard drive clusters 
+    are of a fixed size determined by the operating system. Most of the time, 
+    when a user saves a file to his or her hard drive, the file is not exactly 
+    the same size as the cluster in which the operating system puts it.
     Furthermore, when a user ``deletes'' a file from his or her hard drive, the
@@
     cluster.
+
+    Artifacts can also be recovered from the computer's memory itself. Cached
+    web documents can often be found here.\cite{ohana13} Browsing history,
+    logon information, and cookies have been detected after private browsing
+    sessions by analyzing a computer's memory. The SQLite databases used by 
+    Chrome and Firefox during browsing sessions are generally only stored in 
+    memory when private browsing is in use, and their residual data could be 
+    detected, as well.\cite{satvat13}
+
+    The Windows pagefile can also reveal private browsing artifacts. This file
+    is where the least recently used pages of memory are stored when too many
+    applications are competing for the computer's physical memory. Browsing
+    history and keywords used in internet search engines have been discovered
+    here.\cite{said11}
 
@@
 
-    \subsection{Tor}
-
     \subsection{Forensic Software}
@@
   \section{Conclusion}
+  With all the ways in which private browsing modes can leak information, it
+  may seem as though they are completely useless. This is not entirely true.
+  While private browsing sessions won't help anyone evade law enforcement, a
+  forensic investigation, or the United States government, they are still good
+  enough to fool most computer users. Nosy roommates, family members, or
+  patrons at the public library are unlikely to go to the lengths discussed in
+  this paper to determine what someone else was doing on the internet.
+
+  That said, private browsing modes don't do much to keep a user's identity
+  private to the outside world. Users seeking this kind of anonymity should 
+  consider using the Tor browser, which employs onion routing to connect them 
+  to their destination server. In this type of routing, a random path from the 
+  user to the destination is constructed, and content is encrypted at each 
+  point in the path. Furthermore, each point (known as a relay or node) only 
+  knows from which relay any given piece of network traffic immediately came 
+  and the next relay to which it is going. It does not know the original source
+  of the network traffic or its final destination. This is what allows users to
+  keep themselves and their activities anonymous using Tor in a way that the 
+  traditional web browsers cannot.\cite{tor13} Of course, this type of browsing
+  can be (ab)used for a whole host of illicit activities, but those are beyond
+  the scope of this paper.
+
+  Until Mozilla, Google, and Microsoft reduce the artifacts leaker by their
+  respective browsers' private modes, users who are concerned about ``local 
+  attackers''---those of the nosy roommate or family member variety who have 
+  physical access to their machine---can do their part to keep their private
+  information secure. Random access memory, where private browsing artifacts
+  have been found, is cleared when a computer is powered down. Shutting down
+  the computer after a private browsing session can reduce or eliminate these
+  artifacts. Hard drive artifacts, however, are nearly impossible to eradicate.
+  The moral of the story is that private browsing is nothing more than a nice
+  illusion useful for fooling the computer-illiterate. At the end of the day,
+  private browsing really isn't that private at all.
 
@@
       ieee-security.org/TC/SPW2013/papers/data/5017a135.pdf}$>$
+    \bibitem{satvat13}
+      Satvat, Kiavash, Matthew Forshaw, Feng Hao, and Ehsan Toreini. ``On The 
+      Privacy of Private Browsing - A Forensic Approach.'' Proceedings of the 
+      8th International Workshop on Data Privacy Management (DPM '13), Royal 
+      Holloway, University of London, Egham, UK. 12-13 Sept. 2013. Web. 9 Dec.
+      2013. $<$\url{http://homepages.cs.ncl.ac.uk/feng.hao/files/DPM13.pdf}$>$ 
+    \bibitem{said11}
+      Said, Huwida, Noora Al Mutawa, Ibtesam Al Awadhi, and Mario Guimaraes.
+      ``Forensic Analysis of Private Browsing Artifacts.'' 7th International
+      Conference on Innovations in Information Technology, Abu Dhabi, United
+      Arab Emirates. 25-27 Apr. 2011. Web. 10 Dec. 2013. $<$\url{http://
+      ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=5893816}$>$
 

### 2013-12-13 finalproject/read_browser_databases.py
start searching disk databases

@@ -1,0 +1,29 @@
+# read_browser_databases
+
+# Processes on-disk SQLite database files for Mozilla Firefox and Google Chrome
+# to search for private browsing artifacts
+
+# Notes: Run using Python 3.3.3; some encrypted Firefox SQLite databases will
+# not open using Python 2.7.6
+
+import sqlite3
+import os
+
+# hard-coded search path - find environment variable
+searchpaths = []
+
+searchpaths.append(r"C:\Users\Ashley\AppData\Local\Mozilla\Firefox\Profiles")
+searchpaths.append(r"C:\Users\Ashley\AppData\Roaming\Mozilla\Firefox\Profiles")
+
+for path in searchpaths:
+	for dirpath, dirnames, filenames in os.walk(path):
+		for file in filenames:
+			if file.endswith("sqlite"):
+				db = os.path.join(dirpath, file)
+				conn = sqlite3.connect(db)
+				cursor = conn.cursor()
+				try:
+					cursor.execute("SELECT name FROM sqlite_master;")
+				except sqlite3.DatabaseError:
+					print("Error reading", db)
+				conn.close()

### 2013-12-13 finalproject/read_browser_databases.py
can read all disk dbs, does nothing with data

@@ -11,7 +11,6 @@ import os
 
 # hard-coded search path - find environment variable
 searchpaths = []
-
 searchpaths.append(r"C:\Users\Ashley\AppData\Local\Mozilla\Firefox\Profiles")
 searchpaths.append(r"C:\Users\Ashley\AppData\Roaming\Mozilla\Firefox\Profiles")
 
@@ -23,7 +22,16 @@ for path in searchpaths:
 				conn = sqlite3.connect(db)
 				cursor = conn.cursor()
 				try:
-					cursor.execute("SELECT name FROM sqlite_master;")
+					cursor.execute("SELECT name FROM sqlite_master WHERE type='table';")
 				except sqlite3.DatabaseError:
 					print("Error reading", db)
+				else:
+					tables = cursor.fetchall()
+					for name in tables:
+						print(name[0])
+						cursor.execute("SELECT sql FROM sqlite_master WHERE type='table' AND tbl_name=?;", name)
+						print(cursor.fetchall())
+						cursor.execute("SELECT * FROM {tablename}".format(tablename=name[0]))
+						print(cursor.fetchone())
+						print()
 				conn.close()

### 2013-12-13 finalproject/read_memory.py
started memory reading

@@ -1,0 +1,28 @@
+# read_memory
+
+# Reads memory maps of Mozilla Firefox and Google Chrome (while they are
+# running) to look for private browsing artifacts
+
+# Note: requires WinAppDbg 1.5 (http://winappdbg.sourceforge.net/Downloads.html)
+# Note: runs using Python 2.7.6. WinAppDbg is not compatible with Python 3.3.3,
+#       and it has no intention of becoming compatible with it.
+
+from winappdbg import System, Process, CrashDump
+import os
+
+system = System()
+executables = []
+executables.append("firefox.exe")
+executables.append("chrome.exe")
+
+
+for task in system:
+	task_name = task.get_filename()
+	print task_name
+	if task_name is None:
+		continue
+	if task_name.find("firefox.exe") is not -1:
+		process = Process(task.get_pid())
+		memory_map = process.get_memory_map()
+		print CrashDump.dump_memory_map(memory_map)
+	

### 2013-12-14 finalproject/paper.tex
added definitions section

@@
 
-    \subsection{What Private Browsing Is Not}
-    The private browsing modes of Firefox, Chrome, and Internet Explorer are
-    designed with the intent of preventing users of the same computer from
-    determining what someone was doing on that computer. They do not attempt
-    to keep a user's internet activities hidden from that user's internet
-    service provider (ISP), and they do not prevent websites from identifying
-    that user.\cite{verdi13}\cite{google13}\cite{ie13}
+	\subsection{Definitions}
+	Many shortcomings of private browsing modes relate to how a computer's 
+	operating system manages memory and disk space. Those who are unfamiliar
+	with these tasks may benefit from the definitions below.
+
+	\begin{description}
+	  \item[Cluster] A group of disk sectors that the operating system
+	  treats as a unit; smallest unit of disk storage that the operating
+	  system can allocate
+	  \item[Disk] The hard drive of a computer; where a user's files and
+	  directories (among other things) are stored
+	  \item[Free space] A cluster that is not allocated to any particular 
+	  file
+	  \item[Page] The smallest unit of memory that the operating system can
+	  allocate; can be temporarily stored on disk to allow the computer to run
+	  more programs at the same time
+	  \item[Slack space] The space between the end of a file and the end of 
+	  the cluster in which it is stored; important in computer forensics for
+	  finding fragments of old files\footnote{Hard drive clusters are of a 
+	  fixed size determined by the operating system. Most of the time, when a 
+	  user saves a file to his or her hard drive, the file is not exactly the 
+	  same size as the cluster in which the operating system puts it. 
+	  Furthermore, when a user ``deletes'' a file from his or her hard drive, 
+	  the file is not really deleted---it is simply marked as available to be
+      overwritten if necessary. If a file is eventually stored on the hard 
+	  drive in a cluster that used to be home to a larger (now ``deleted'') 
+	  file, leftover data from the old file will still exist at the end of that
+      cluster.}
+	\end{description}
 
@@
     history, and cached images were recovered obtained most of the artifacts
-    from portions of the hard disk known as \emph{free space} and \emph{slack
-    space}.\cite{ohana13} Free space refers to a group of hard drive sectors 
-    (called a \emph{cluster}) that is not allocated to any particular file.
-    Slack space,on the other hand, refers to the space between the end of a 
-    file and the end of the cluster in which it is stored. Hard drive clusters 
-    are of a fixed size determined by the operating system. Most of the time, 
-    when a user saves a file to his or her hard drive, the file is not exactly 
-    the same size as the cluster in which the operating system puts it.
-    Furthermore, when a user ``deletes'' a file from his or her hard drive, the
-    file is not really deleted---it is simply marked as available to be
-    overwritten if necessary. If a file is eventually stored on the hard drive
-    in a cluster that used to be home to a larger (now ``deleted'') file,
-    leftover data from the old file will still exist at the end of that
-    cluster.
+    from the hard drive's free space and slack space.\cite{ohana13}
 
@@
     \subsection{Firefox}
+	In 2011, researchers discovered that Firefox 3.6.11 stored browser history
+	and search engine keywords in the computer's physical memory and that this
+	information could be accessed after the browsing session was terminated.
+	An analysis of the contents of pagefile.sys revealed similar information.
+	\cite{said11} Additionally, certificate chains received during private 
+	browsing sessions in Firefox 3.6 were not removed from their on-disk 
+	database once the browsing session was terminated.
 

### 2013-12-14 finalproject/paper.tex
started adding specific browser flaws

@@
     \end{center}
+
     \doublespacing
-
 	\subsection{Definitions}
@@
 	  system can allocate
+	  \item[Digital certificate] Verifies that a particular website or target
+	  server is who it claims to be when connecting securely
 	  \item[Disk] The hard drive of a computer; where a user's files and
@@
     \subsection{Where To Look}
-    Focused analysis of the hard drive itself can reveal the most artifacts.
+    Focused analysis of the hard drive can reveal the most artifacts.
     One private browsing experiment in which logon information, browser
     history, and cached images were recovered obtained most of the artifacts
-    from the hard drive's free space and slack space.\cite{ohana13}
+    from the hard drive's free space and slack space.\cite{ohana13} The 
+	Windows pagefile (pagefile.sys on the hard drive) in particular can reveal
+	private browsing artifacts. This file is where the least recently used 
+	pages of memory are stored when too many applications are competing for the
+	computer's physical memory. Browsing history and keywords used in internet 
+	search engines have been discovered here.\cite{said11}
 
@@
 
-    The Windows pagefile can also reveal private browsing artifacts. This file
-    is where the least recently used pages of memory are stored when too many
-    applications are competing for the computer's physical memory. Browsing
-    history and keywords used in internet search engines have been discovered
-    here.\cite{said11}
-
     \subsection{Firefox}
@@
 	An analysis of the contents of pagefile.sys revealed similar information.
-	\cite{said11} Additionally, certificate chains received during private 
+	\cite{said11} Additionally, digital certificates received during private 
 	browsing sessions in Firefox 3.6 were not removed from their on-disk 
-	database once the browsing session was terminated.
+	database once the browsing session was terminated.\cite{aggarwal10}
 
     \subsection{Google Chrome}
+    One 2013 study stated that it was more difficult to retrieve private
+	browsing artifacts from Chrome's incognito mode than Firefox or Internet
+	Explorer.\cite{said11}
 
@@
     Internet Explorer leaves the most artifacts behind when its InPrivate
-    Browsing mode terminates.\cite{ohana13}
+    Browsing mode terminates.\cite{ohana13} Internet Explorer 8.0.6001.18702
+	continued to cache web pages on the hard drive during an InPrivate
+	Browsing session, but these files were deleted once the browser window was
+	closed. This means that fragments of these files---and thus a record of the
+	user's browsing history---could be discovered by analyzing the free and
+	slack space of the hard drive.\cite{said11}
 
@@
   \begin{thebibliography}{9}
-    \bibitem{verdi13}
-      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
-      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
-      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
-      without-saving-info}$>$.
+	\bibitem{aggarwal10}
+	  Aggarwal, Gaurav, Elie Bursztein, Collin Jackson, and Dan Boneh.
+	  ``An Analysis of Private Browsing Modes in Modern Browsers.''
+	  Proceedings of the 19th USENIX Security Symposium,  Wardman Park Marriott
+	  Hotel, Washington, D.C. 11-13 Aug. 2013. Web. 8 Dec. 2013. $<$
+	  \url{http://crypto.stanford.edu/~dabo/pubs/papers/privatebrowsing.pdf}$>$
     \bibitem{google13}
@@
       internet-explorer/products/ie-9/features/in-private}$>$.
-    \bibitem{tor13}
-      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
-      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$. 
     \bibitem{ohana13}
@@
       ieee-security.org/TC/SPW2013/papers/data/5017a135.pdf}$>$
+    \bibitem{said11}
+      Said, Huwida, Noora Al Mutawa, Ibtesam Al Awadhi, and Mario Guimaraes.
+      ``Forensic Analysis of Private Browsing Artifacts.'' 7th International
+      Conference on Innovations in Information Technology, Abu Dhabi, United
+      Arab Emirates. 25-27 Apr. 2011. Web. 10 Dec. 2013. $<$\url{http://
+      ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=5893816}$>$ 
     \bibitem{satvat13}
@@
       2013. $<$\url{http://homepages.cs.ncl.ac.uk/feng.hao/files/DPM13.pdf}$>$ 
-    \bibitem{said11}
-      Said, Huwida, Noora Al Mutawa, Ibtesam Al Awadhi, and Mario Guimaraes.
-      ``Forensic Analysis of Private Browsing Artifacts.'' 7th International
-      Conference on Innovations in Information Technology, Abu Dhabi, United
-      Arab Emirates. 25-27 Apr. 2011. Web. 10 Dec. 2013. $<$\url{http://
-      ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=5893816}$>$
-
+	\bibitem{tor13}
+      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
+      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$. 
+	\bibitem{verdi13}
+      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
+      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
+      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
+      without-saving-info}$>$.
   \end{thebibliography}
-
 \end{document}

### 2013-12-15 finalproject/read_browser_databases.py
added environment variables

@@ -9,10 +9,16 @@
 import sqlite3
 import os
 
-# hard-coded search path - find environment variable
+user = os.environ.get(r"USERPROFILE")
+if user is None:
+	print("Error: cannot access user's directory")
+	exit(1)
+	
 searchpaths = []
-searchpaths.append(r"C:\Users\Ashley\AppData\Local\Mozilla\Firefox\Profiles")
-searchpaths.append(r"C:\Users\Ashley\AppData\Roaming\Mozilla\Firefox\Profiles")
+prefix = os.getenv(r"LOCALAPPDATA", r"{user}\AppData\Local".format(user=user))
+searchpaths.append("{start}\Mozilla\Firefox\Profiles".format(start=prefix))
+prefix = os.getenv(r"APPDATA", r"{user}\AppData\Roaming".format(user=user))
+searchpaths.append(r"{start}\Mozilla\Firefox\Profiles".format(start=prefix))
 
 for path in searchpaths:
 	for dirpath, dirnames, filenames in os.walk(path):

### 2013-12-15 finalproject/paper.tex
finished browser problems

@@
   and digital media such as images and videos---all items that you would expect
-  a private browsing session to keep private.\cite{ohana13}
-
-  This section will first summarize locations on a Windows machine where
-  private browsing artifacts might be found. An overview of what specific
-  artifacts were found for each browser using different forensic techniques
-  will follow. The use of SQLite to investigate specific browser artifacts will
-  then be discussed.
+  a private browsing session to keep private.\cite{ohana13} Private browsing
+  sessions can be exploited by browser extensions and remote attacks, but this 
+  section will focus on artifacts left on a local machine by the browsers 
+  themselves.
 
@@
     An analysis of the contents of pagefile.sys revealed similar information.
-	\cite{said11} Additionally, digital certificates received during private 
-	browsing sessions in Firefox 3.6 were not removed from their on-disk 
-	database once the browsing session was terminated.\cite{aggarwal10}
+    \cite{said11} The presence of these in-memory artifacts persisted through 
+    Firefox 17.0.1.\cite{ohana13} Additionally, digital certificates received 
+    during private browsing sessions in Firefox 3.6 were not removed from their 
+    on-disk database once the browsing session was terminated.\cite{aggarwal10}
+
+    Researchers demonstrated in 2013 that on-disk files used by Firefox 17.0.1 
+    showed modified timestamps after a private browsing session. Even though
+    information about the user's activities may not be directly accessible,
+    evidence that a private browsing session took place can help forensic
+    investigators determine why browsing history cannot easily be located on a
+    suspect's machine, especially when analysis of the computer's memory is not
+    possible.\cite{ohana13} Firefox 19.0 fixed this problem.\cite{satvat13}
 
     \subsection{Google Chrome}
-    One 2013 study stated that it was more difficult to retrieve private
-	browsing artifacts from Chrome's incognito mode than Firefox or Internet
-	Explorer.\cite{said11}
+    One 2011 study stated that it was more difficult to retrieve private
+    browsing artifacts from Chrome's incognito mode (using Chrome 7.0.517.41) 
+    than Firefox or Internet Explorer. That study found that, as in Firefox 
+    3.6.11, browsing history and search engine keywords could be accessed in 
+    the computer's memory after the incognito session terminated. However, it 
+    found no on-disk artifacts. Only physical memory contained these artifacts, 
+    as the pagefile revealed no traces of the websites visited or searches 
+    performed using incognito mode.\cite{said11}
+
+    Chrome 23.0.1271.95, on the other hand, modified timestamps for many files
+    when terminating incognito sessions. As with Chrome 7.0.517.41, artifacts 
+    related to the user's browsing activities were limited to the computer's 
+    memory. However, the pagefile did reveal evidence of a file downloaded
+    during an incognito browsing session.\cite{ohana13} The timestamp artifacts
+    were still present as of version 25.0.1364.97.\cite{satvat13}
 
@@
     user's browsing history---could be discovered by analyzing the free and
-	slack space of the hard drive.\cite{said11}
+    slack space of the hard drive.\cite{said11} Login information for email
+    accounts and full image artifacts were discovered on the machine after an 
+    InPrivate Browsing session using Internet Explorer 8.0 as recently as 2013.
+    \cite{ohana13} Researchers recently determined that Internet Explorer log 
+    files no longer contained evidence of browsing history as of version 
+    10.0.9200.16521. This had been an issue in previous versions of the 
+    browser.\cite{satvat13}
 

### 2013-12-15 finalproject/paper.tex
preparing to recompile pdf

@@
     computer's physical memory. Browsing history and keywords used in internet 
-    search engines have been discovered here.\cite{said11}
+    search engines have been discovered here.\cite{said11} Free programs such 
+	as \href{http://www.sleuthkit.org/autopsy/}{Autopsy} allow anyone to 
+	investigate the free and slack space of a hard drive.
 
@@
     browser.\cite{satvat13}
-
-    \subsection{Forensic Software}
 

### 2013-12-15 finalproject/paper.tex
updated pdf

@@
 \setlength\parindent{0.5in}
+\doublespacing
 
@@
   already demonstrated methods of detecting this information. These include the
-  analysis of virtual and browser memory and the pagefile on Windows machines.
+  analysis of the hard drive, memory, and the pagefile on Windows machines.
   The existence of private browsing artifacts on a user’s machine raises many 
@@
   end user? And, if the user’s browsing session can be reconstructed from these 
-  artifacts, how might this be exploited by digital forensics professionals? 
-  This paper seeks to answer these questions and to prove that such artifacts 
-  can be used to determine, at least in part, what a user was doing during his 
-  or her ``private browsing'' session---thereby rendering it not very private 
-  at all.
+  artifacts, how much information would digital forensics professionals be 
+  able to gain? This paper seeks to answer these questions and to prove that 
+  such artifactscan be used to determine, at least in part, what a user was 
+  doing during his or her ``private browsing'' session---thereby rendering it 
+  not very private at all.
   \end{abstract}
 
-  \doublespacing
   \section{Introduction}
@@
     Explorer. All three of these browsers have built-in private browsing modes.
-    The features and protections provided by each of these private browsing
-    modes are summarized below.\cite{verdi13}\cite{google13}\cite{ie13}
+    While they all have different names---``Private Browsing'' in Firefox,
+    ``Incognito Mode'' in Chrome, and ``InPrivate Browsing'' in Internet
+    Explorer---they all claim to do essentially the same thing: allow a user to
+    browse the web without traces of his or her browsing history, login
+    information, form and search bar entries, or downloads remaining on his or
+    her machine.\cite{verdi13}\cite{google13}\cite{ie13}
 
-    \singlespacing
-    \begin{center}
-      \begin{tabular}{|p{5cm}|c|c|c|}
-        \hline
-         & Firefox & Chrome & Internet Explorer \\
-         & Private Browsing & Incognito Mode & InPrivate Browsng \\
-        \hline
-        Browser history & X & X & X \\
-        \hline
-        Form data & X &  & X \\
-        \hline
-        Search bar data & X &  & X \\
-        \hline
-        Passwords & X &  & X \\
-        \hline
-        Downloads & X & X &  \\
-        \hline
-        Cookies & X & X & X \\
-        \hline
-        Cached files & X &  & X \\
-        \hline
-        Simulataneous sessions with different privacy settings & X & X & X \\
-        \hline
-      \end{tabular}
-    \end{center}
-
-    \doublespacing
     \subsection{Definitions}
@@
 
-    \begin{description}
-      \item[Cluster] A group of disk sectors that the operating system
+    \singlespacing
+    \begin{itemize}
+      \item \emph{Cluster}: A group of disk sectors that the operating system
       treats as a unit; smallest unit of disk storage that the operating
       system can allocate
-      \item[Digital certificate] Verifies that a particular website or target
-      server is who it claims to be when connecting securely
-      \item[Disk] The hard drive of a computer; where a user's files and
+      \item \emph{Digital certificate}: Verifies that a particular website or 
+      target server is who it claims to be when connecting securely
+      \item \emph{Disk}: The hard drive of a computer; where a user's files and
       directories (among other things) are stored
-      \item[Free space] A cluster that is not allocated to any particular 
-      file
-      \item[Page] The smallest unit of memory that the operating system can
-      allocate; can be temporarily stored on disk to allow the computer to run
-      more programs at the same time
-      \item[Slack space] The space between the end of a file and the end of 
-      the cluster in which it is stored; important in computer forensics for
+      \item \emph{Free space}: A cluster that is not allocated to any 
+      particular file
+      \item \emph{Page}: The smallest unit of memory that the operating system 
+      can allocate; can be temporarily stored on disk to allow the computer to 
+      run more programs at the same time
+      \item \emph{Slack space}: The space between the end of a file and the end
+      of the cluster in which it is stored; important in computer forensics for
       finding fragments of old files\footnote{Hard drive clusters are of a 
@@
       cluster.}
-    \end{description}
+    \end{itemize}
 
+  \doublespacing
   \section{To the Community}
@@
   and digital media such as images and videos---all items that you would expect
-  a private browsing session to keep private.\cite{ohana13} Private browsing
-  sessions can be exploited by browser extensions and remote attacks, but this 
-  section will focus on artifacts left on a local machine by the browsers 
-  themselves.
+  a private browsing session to keep private. Additionally, browser extensions 
+  can often record this kind of information, even when a user is browsing 
+  privately.
 
@@
     browser.\cite{satvat13}
+
+    %\subsection{Browser Extensions}
+    % Write me!
 

### 2013-12-15 finalproject/read_browser_databases.py
added tests to database reading

@@ -1,43 +1,117 @@
 # read_browser_databases
 
-# Processes on-disk SQLite database files for Mozilla Firefox and Google Chrome
+# Processes on-disk SQLite database files for Mozilla Firefox
 # to search for private browsing artifacts
 
 # Notes: Run using Python 3.3.3; some encrypted Firefox SQLite databases will
 # not open using Python 2.7.6
 
 import sqlite3
+import sys
 import os
+import time
 
-user = os.environ.get(r"USERPROFILE")
-if user is None:
-	print("Error: cannot access user's directory")
-	exit(1)
-	
-searchpaths = []
-prefix = os.getenv(r"LOCALAPPDATA", r"{user}\AppData\Local".format(user=user))
-searchpaths.append("{start}\Mozilla\Firefox\Profiles".format(start=prefix))
-prefix = os.getenv(r"APPDATA", r"{user}\AppData\Roaming".format(user=user))
-searchpaths.append(r"{start}\Mozilla\Firefox\Profiles".format(start=prefix))
-
-for path in searchpaths:
+def run_tests():
+	current_time = int(time.time() * 1000000 - 3600000000)
+	print(current_time)
+	user = os.environ.get(r"USERPROFILE")
+	if user is None:
+		print("Error: cannot access user's directory")
+		exit(1)
+	print("The following is a selection of things that might be interesting.")
+	print("False positives may appear if non-private browsing used in last hour.")
+	print()
+		
+	prefix = os.getenv(r"APPDATA", r"{user}\AppData\Roaming".format(user=user))
+	path = r"{start}\Mozilla\Firefox\Profiles".format(start=prefix)
 	for dirpath, dirnames, filenames in os.walk(path):
 		for file in filenames:
-			if file.endswith("sqlite"):
+			if file == "cookies.sqlite":
+				print("\n---Cookies created in last hour---")
+				print("If a user is currently using private browsing, cookies will show up here.")
+				print("If a user terminated a private browsing session in the last hour, they may not.")
 				db = os.path.join(dirpath, file)
 				conn = sqlite3.connect(db)
 				cursor = conn.cursor()
-				try:
-					cursor.execute("SELECT name FROM sqlite_master WHERE type='table';")
-				except sqlite3.DatabaseError:
-					print("Error reading", db)
-				else:
-					tables = cursor.fetchall()
-					for name in tables:
-						print(name[0])
[…]

### 2013-12-15 finalproject/read_memory.py
this freezes computers do not run

@@ -1,28 +1,53 @@
 # read_memory
 
-# Reads memory maps of Mozilla Firefox and Google Chrome (while they are
+# Reads memory maps of Mozilla Firefox (while they are
 # running) to look for private browsing artifacts
 
 # Note: requires WinAppDbg 1.5 (http://winappdbg.sourceforge.net/Downloads.html)
 # Note: runs using Python 2.7.6. WinAppDbg is not compatible with Python 3.3.3,
 #       and it has no intention of becoming compatible with it.
 
-from winappdbg import System, Process, CrashDump
+from winappdbg import System, Process, CrashDump, HexDump
 import os
+import sys
+
+# Checks to be sure we're running on Windows with Python 2.7.6
+if sys.platform != "win32":
+    print("Error: This program runs on Windows.")
+    exit(1)
+version = sys.version_info
+if (version.major, version.minor, version.micro) != (2, 7, 6):
+    print("Error: This program is written for Python 2.7.6")
+    print("You are running:", version.major, ".", version.minor, ".", version.micro)
+    exit(1)
 
 system = System()
-executables = []
-executables.append("firefox.exe")
-executables.append("chrome.exe")
+#executables = []
+#executables.append("firefox.exe")
+#executables.append("chrome.exe")
 
 
 for task in system:
-	task_name = task.get_filename()
-	print task_name
-	if task_name is None:
-		continue
-	if task_name.find("firefox.exe") is not -1:
-		process = Process(task.get_pid())
-		memory_map = process.get_memory_map()
-		print CrashDump.dump_memory_map(memory_map)
-	
+    task_name = task.get_filename()
+    if task_name is None:
+        continue
+    if task_name.find("firefox.exe") != -1:
+        process = Process(task.get_pid())
+        memory_map = process.get_memory_map()
+        list = process.take_memory_snapshot()
+        for item in list:
+            print item.filename, item.content
+        
+        bits = process.get_bits()
+        # for mbi in memory_map:
+            # base_address = mbi.BaseAddress
+            # region_size  = mbi.RegionSize
+            # data = None
+            # if mbi.has_content():
+                # data = process.read(base_address, region_size)
+                # print data
+            
+        #print CrashDump.dump_memory_map(memory_map)
+        #for address, size, data in process.strings():
+            #print HexDump.address(address), data
+    

### 2013-12-15 finalproject/read_browser_databases.py
added basic interactive mode

@@ -62,7 +62,7 @@ def interact():
 	searchpaths.append(r"{start}\Mozilla\Firefox\Profiles".format(start=prefix))
 
 	# Finds available tables
-	tables = []
+	db_map = {}
 	for path in searchpaths:
 		for dirpath, dirnames, filenames in os.walk(path):
 			for file in filenames:
@@ -75,25 +75,36 @@ def interact():
 					except sqlite3.DatabaseError:
 						print("Error reading", db)
 					else:
-						tables.append(cursor.fetchall())
+						for table in cursor.fetchall():
+							print(table)
+							db_map[table[0]] = db
 					conn.close()
 	
 	finished = False
 	while not finished:
 		print("Type a table name to view its data.")
-		for name in tables:
+		for name in db_map:
 			print(name)
 		choice = input("View table (or Q to quit): ")
 		if choice == "Q":
 			finished = True
 			continue
-		if choice not in tables:
+		if choice not in db_map:
 			print("Error: Not a valid table.")
 			continue
 		else:
-			print("Error: Not yet implemented.")
-		# Realized that this doesn't associate table names with files. Hmm.
+			conn = sqlite3.connect(db_map[choice])
+			cursor = conn.cursor()
+			# Should use a try-except here
+			cursor.execute("SELECT * FROM {table}".format(table=choice))
+			for item in cursor.fetchall():
+				print(item)
+			conn.close()
+			if input("Hit any key to continue (or Q to quit)") == "Q":
+				finished = True
+	exit(0)
 
+# MAIN
 # Checks to be sure we're running on Windows with Python 3.3.3
 if sys.platform != "win32":
 	print("Error: This program runs on Windows.")

### 2013-12-15 finalproject/read_memory.py
edits all over the place

@@ -1,4 +1,5 @@
 # read_memory
+# read_memory
 
 # Reads memory maps of Mozilla Firefox (while they are
 # running) to look for private browsing artifacts
@@ -33,21 +34,10 @@ for task in system:
         continue
     if task_name.find("firefox.exe") != -1:
         process = Process(task.get_pid())
-        memory_map = process.get_memory_map()
-        list = process.take_memory_snapshot()
-        for item in list:
-            print item.filename, item.content
-        
-        bits = process.get_bits()
-        # for mbi in memory_map:
-            # base_address = mbi.BaseAddress
-            # region_size  = mbi.RegionSize
-            # data = None
-            # if mbi.has_content():
-                # data = process.read(base_address, region_size)
-                # print data
-            
-        #print CrashDump.dump_memory_map(memory_map)
-        #for address, size, data in process.strings():
-            #print HexDump.address(address), data
+        #memory_map = process.get_memory_map()
+		
+		# Convert this to logging of some sort
+		# And only print URL-like things?
+        for address, size, data in process.strings():
+            print HexDump.address(address), HexDump.printable(data)
     

### 2013-12-15 finalproject/paper.tex
edits all over the place
almost done (need to re-export pdf and clean up)

@@
 
-    %\subsection{Browser Extensions}
-    % Write me!
+	\subsection{Proof of Concept: Parsing SQLite Databases and Browser Memory}
+	% find paper that had the thing about no last visited date and cite
+	As an example of the persistence of some of these private browsing 
+	shortcomings, two Python scripts were written to accompany this paper.
+	The first parses the SQLite databases of Mozilla Firefox to look for 
+	private browsing artifacts. There are two built-in artifact searches. It 
+	will print any cookies created within the last hour; if private browsing is
+	currently in use, some cookies may show up here before being removed upon
+	browser termination. Additionally, URLs that have a nonzero access count
+	but an unspecified last visit time will be printed. It cannot be easily
+	determined when these websites were visited, but it is likely that it was
+	during a private browsing session. Upon manual review of the URLs retrieved 
+	from this database, URLs visited more recently during a private browsing 
+	session appeared at the bottom of the list. The 
+	\href{https://addons.mozilla.org/en-US/firefox/addon/sqlite-manager}
+	{SQLite Manager} extension for Firefox was used to discover these possible
+	artifact sources before a programmatic solution was implemented.
+
+	The second script retrieves the contents of the memory segments associated
+	with a running Firefox or Chrome process.
+	%Finish this
 
@@
   artifacts. Hard drive artifacts, however, are nearly impossible to eradicate.
-  The moral of the story is that private browsing is nothing more than a nice
-  illusion useful for fooling the computer-illiterate. At the end of the day,
-  private browsing really isn't that private at all.
+  Even if the files whose timestamps were updated upon termination of a 
+  private browsing session could be deleted without affecting the browser, 
+  their fragments would still remain on the hard drive. The moral of the story 
+  is that private browsing is nothing more than a nice illusion useful for 
+  fooling the computer-illiterate. At the end of the day, private browsing 
+  really isn't that private at all.
 

### 2013-12-15 finalproject/read_memory.py

@@ -8,7 +8,7 @@
 # Note: runs using Python 2.7.6. WinAppDbg is not compatible with Python 3.3.3,
 #       and it has no intention of becoming compatible with it.
 
-from winappdbg import System, Process, CrashDump, HexDump
+from winappdbg import System, Process, HexDump
 import os
 import sys
 
@@ -23,21 +23,18 @@ if (version.major, version.minor, version.micro) != (2, 7, 6):
     exit(1)
 
 system = System()
-#executables = []
-#executables.append("firefox.exe")
-#executables.append("chrome.exe")
-
 
 for task in system:
     task_name = task.get_filename()
     if task_name is None:
         continue
-    if task_name.find("firefox.exe") != -1:
-        process = Process(task.get_pid())
-        #memory_map = process.get_memory_map()
-		
-		# Convert this to logging of some sort
-		# And only print URL-like things?
-        for address, size, data in process.strings():
-            print HexDump.address(address), HexDump.printable(data)
+    if (task_name.find("firefox.exe") != -1) or (task_name.find("chrome.exe") != -1):
+        process = Process(task.get_pid())   
+        filename = "{executable}_output.txt".format(executable=task_name)
+        with open(filename, "w") as f:
+            for address, size, data in process.strings():
+                tuple = (HexDump.address(address), HexDump.printable(data))
+                f.write(str(tuple))
+                if tuple[1].startswith((r"http://", r"https://")):
+                    print tuple
     

### 2013-12-16 finalproject/paper.tex
cleaned code, wrote last paragraph

@@
 	\subsection{Proof of Concept: Parsing SQLite Databases and Browser Memory}
-	% find paper that had the thing about no last visited date and cite
 	As an example of the persistence of some of these private browsing 
@@
 	The second script retrieves the contents of the memory segments associated
-	with a running Firefox or Chrome process.
-	%Finish this
+	with a running Firefox or Chrome process. String literals in the browser's
+	memory are then logged to an output file, separated by browser.
+	Additionally, potentially interesting memory contents (currently URLs, but
+	could easily be modified to include other items of interest) are printed to
+	the terminal. This was accomplished using the 
+	\href{http://winappdbg.sourceforge.net/}{WinAppDbg} module.
 

### 2013-12-16 finalproject/read_browser_databases.py

@@ -1,118 +1,122 @@
 # read_browser_databases
 
-# Processes on-disk SQLite database files for Mozilla Firefox
-# to search for private browsing artifacts
+# Processes on-disk SQLite database files for Mozilla Firefox to search for
+# private browsing artifacts
 
-# Notes: Run using Python 3.3.3; some encrypted Firefox SQLite databases will
-# not open using Python 2.7.6
+# Notes: Run using Python 3.3.3; some Firefox SQLite databases will not open 
+# using Python 2.7.6
 
 import sqlite3
 import sys
 import os
 import time
 
+# run_tests - prints potentially interesting data to terminal
 def run_tests():
-	current_time = int(time.time() * 1000000 - 3600000000)
-	print(current_time)
-	user = os.environ.get(r"USERPROFILE")
-	if user is None:
-		print("Error: cannot access user's directory")
-		exit(1)
-	print("The following is a selection of things that might be interesting.")
-	print("False positives may appear if non-private browsing used in last hour.")
-	print()
-		
-	prefix = os.getenv(r"APPDATA", r"{user}\AppData\Roaming".format(user=user))
-	path = r"{start}\Mozilla\Firefox\Profiles".format(start=prefix)
-	for dirpath, dirnames, filenames in os.walk(path):
-		for file in filenames:
-			if file == "cookies.sqlite":
-				print("\n---Cookies created in last hour---")
-				print("If a user is currently using private browsing, cookies will show up here.")
-				print("If a user terminated a private browsing session in the last hour, they may not.")
-				db = os.path.join(dirpath, file)
-				conn = sqlite3.connect(db)
-				cursor = conn.cursor()
-				cursor.execute("SELECT * FROM moz_cookies WHERE creationTime >= ?", (current_time,))
-				print(cursor.fetchall())
-			if file == "places.sqlite":
-				print("\n---Places with unknown visit times---")
-				print("Displays URLs with no last visit date but nonzero frequencies")
-				print("Entries toward bottom of list are likely more recent.")
-				db = os.path.join(dirpath, file)
-				conn = sqlite3.connect(db)
-				cursor = conn.cursor()
-				# Why Firefox named this column "frecency", I have no idea...
-				cursor.execute("SELECT url FROM moz_places WHERE frecency > 0 AND last_visit_date IS NULL")
-				for item in cursor.fetchall():
-					print(item[0])
-				
-	exit(0)
[…]

### 2013-12-16 finalproject/read_memory.py

@@ -1,7 +1,6 @@
 # read_memory
-# read_memory
 
-# Reads memory maps of Mozilla Firefox (while they are
+# Reads memory maps of Mozilla Firefox and Google Chrome (while they are
 # running) to look for private browsing artifacts
 
 # Note: requires WinAppDbg 1.5 (http://winappdbg.sourceforge.net/Downloads.html)
@@ -22,19 +21,25 @@ if (version.major, version.minor, version.micro) != (2, 7, 6):
     print("You are running:", version.major, ".", version.minor, ".", version.micro)
     exit(1)
 
+# Retrieves system snapshot and iterates through running tasks
 system = System()
-
 for task in system:
     task_name = task.get_filename()
     if task_name is None:
         continue
     if (task_name.find("firefox.exe") != -1) or (task_name.find("chrome.exe") != -1):
+		# Obtains memory information about currently running browser
         process = Process(task.get_pid())   
-        filename = "{executable}_output.txt".format(executable=task_name)
+        filename = ""
+        if task_name.find("firefox.exe") != -1:
+            filename = "firefox_output.txt"
+        else:
+            filename = "chrome_output.txt"
         with open(filename, "w") as f:
+			# Extracts all string literals from memory
+			# All strings are logged, while URLs are printed to terminal
             for address, size, data in process.strings():
                 tuple = (HexDump.address(address), HexDump.printable(data))
                 f.write(str(tuple))
                 if tuple[1].startswith((r"http://", r"https://")):
                     print tuple
-    

### 2013-12-16 finalproject/read_memory.py
fixed read memory output format

@@ -40,6 +40,6 @@ for task in system:
 			# All strings are logged, while URLs are printed to terminal
             for address, size, data in process.strings():
                 tuple = (HexDump.address(address), HexDump.printable(data))
-                f.write(str(tuple))
-                if tuple[1].startswith((r"http://", r"https://")):
-                    print tuple
+                f.write(tuple[0] + "\t" + tuple[1] + "\n")
+                if tuple[1].startswith((r"http://", r"https://", r"HTTP-memory-only")):
+                    print tuple[0], "\t", tuple[1]

### 2013-12-16 finalproject/paper.tex
regenerated paper

@@
 \begin{document}
-  \singlespacing
   \title{The Privacy of Private Browsing}
@@
   analysis of the hard drive, memory, and the pagefile on Windows machines.
-  The existence of private browsing artifacts on a user’s machine raises many 
+  The existence of private browsing artifacts on a user's machine raises many 
   questions: how much privacy do web browser developers actually aim to provide
@@
   able to gain? This paper seeks to answer these questions and to prove that 
-  such artifactscan be used to determine, at least in part, what a user was 
+  such artifacts can be used to determine, at least in part, what a user was 
   doing during his or her ``private browsing'' session---thereby rendering it 
@@
 
-    \subsection{Firefox}
+    \subsection{Mozilla Firefox}
     In 2011, researchers discovered that Firefox 3.6.11 stored browser history
@@
 
-    \subsection{Internet Explorer}
+    \subsection{Microsoft Internet Explorer}
     Internet Explorer leaves the most artifacts behind when its InPrivate
